Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-08 numerical-mhd-dedner.tex
Fixed some refs

For the reconstruction scheme we here implemented only the simple
piecewise linear reconstruction \citep{
And a number of approximate Riemann
solvers.

>>>>

For the reconstruction scheme we here implemented only the simple
piecewise linear reconstruction \citep{1979JCoPh..32..101V}.
And a number of approximate Riemann
solvers.
